KidsAIR: exposure model

### 2020-05-22 collinearity_exposure_analysis.Rmd
exposure analysis/model updates

```{r, eval=TRUE, include=TRUE}
####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # dichotomize variables by median value
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  mutate(home_act_door_2level = cut(home_act_door_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep_sum, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))
```

@@

```{r, eval=TRUE, include=TRUE}
# Filter data for specific variables; select pm variable
pm_mean_sampling_period <- analysis_data %>% 
  select(pm_mean_sampling_period, 
         income_3level, 
         residents_smoke,
         home_year_built_2level,
         home_floors_2level, 
         home_pets_2level,
         stove_age_3level,
         chimney_clean_3level, 
         home_fireplace,
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(pm_mean_sampling_period)

# Filter data for specific variables; select predictor variables
other_vars <- analysis_data %>% 
  select(pm_mean_sampling_period, 
         income_3level, 
         residents_smoke,
         home_year_built_2level,
         home_floors_2level, 
         home_pets_2level,
         stove_age_3level,
         chimney_clean_3level, 
         home_fireplace,
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(-pm_mean_sampling_period)

@@

Initially assessed the following variables for collinearity, based on simple
associations with mean PM over the sampling period:
         pm_mean_sampling_period, income_3level, area,
         residents_smoke,
         home_floors_2level, 
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         stove_cert, home_mold,
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         home_act_smoke_2level, 
         home_act_door_2level,
         stove_grade_3level,
         race_parent_2level, home_damp, 
         temp_max_5, home_act_gas, home_type_2level, 
         home_windows_2level, home_fireplace

>>>>

```{r, eval=TRUE, include=TRUE}
####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo" & area == "WMT") %>% 
  filter(home != "WMA300") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # dichotomize variables by median value
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  mutate(home_act_door_2level = cut(home_act_door_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep_sum, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))
```

@@

```{r, eval=TRUE, include=TRUE}
# Filter data for specific variables; select pm variable
pm_mean_sampling_period <- analysis_data %>% 
  select(pm_mean_sampling_period, 
         income_3level,
         residents_smoke,
         home_floors_2level, 
         home_sqft_2level,
         home_pets_2level,
         stove_age_3level, 
         chimney_clean_3level, 
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(pm_mean_sampling_period)

# Filter data for specific variables; select predictor variables
other_vars <- analysis_data %>% 
  select(pm_mean_sampling_period, 
         income_3level,
         residents_smoke,
         home_floors_2level, 
         home_sqft_2level,
         home_pets_2level,
         stove_age_3level, 
         chimney_clean_3level, 
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(-pm_mean_sampling_period)

@@

Initially assessed the following variables for collinearity, based on simple
associations with mean PM over the sampling period:
         pm_mean_sampling_period, income_3level, area,
         residents_smoke,
         home_floors_2level, home_sqft_2level,
         home_pets_2level,
         stove_age_3level, chimney_clean_3level, 
         stove_cert, 
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         home_act_smoke_2level, 
         stove_grade_3level,
         race_parent_2level, residents_under5_2level,
         home_type_2level, 
         home_fireplace

### 2020-05-22 dustrak_data_cleaning.Rmd
exposure analysis/model updates

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "501", location = "WMT")
head(gaps, 25)
head(pm_desc, 25)
tail(pm_desc, 25)

# filter data for a single home
check_data <- kids_pm %>% 
  filter(area == "WMT" & home_winter_id == "129") %>% 
  filter(pm < 0)
```

>>>>

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "259", location = "WMT")
head(gaps, 25)
head(pm_desc, 25)
tail(pm_desc, 25)

ggsave("wmt_hwid259_high_pm.jpeg")

# filter data for a single home
check_data <- kids_pm %>% 
  filter(area == "WMT" & home_winter_id == "137") %>% 
  filter(pm < 0)
```

### 2020-05-22 exposure_covariate_associations.Rmd
exposure analysis/model updates

```{r, eval=TRUE, include=TRUE}
####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # dichotomize variables by median value
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  mutate(home_act_door_2level = cut(home_act_door_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep_sum, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))

@@

>>>>

```{r, eval=TRUE, include=TRUE}
####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # dichotomize variables by median value
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  mutate(home_act_door_2level = cut(home_act_door_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep_sum, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))

@@

  print(table(model.frame(analysis_results)$analysis_covar))
  #print(nobs(analysis_results))

### 2020-05-22 exposure_models.Rmd
exposure analysis/model updates

```{r}
####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # dichotomize variables by median value
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  mutate(home_act_door_2level = cut(home_act_door_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep_sum, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))
```

@@

# Select analysis vars
selected_vars <- analysis_data %>% 
  filter(area == "WMT") %>% 
  select(pm_mean_sampling_period, 
         income_3level, 
         residents_smoke,
         home_year_built_2level,
         home_floors_2level, 
         home_pets_2level,
         stove_age_3level,
         chimney_clean_3level, 
         home_fireplace,
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period)) %>% 
  select(-pm_mean_sampling_period) 
```

@@

# Check % missing data
mean(is.na(selected_vars)) # 10%

@@

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_grade_3level), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary

# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_grade_3level), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

@@

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(mean_temp_sampling_period_5, na.rm = TRUE), 
            sd_var = sd(mean_temp_sampling_period_5, na.rm = TRUE),
            median_var = median(mean_temp_sampling_period_5, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(mean_temp_sampling_period_5, na.rm = TRUE), 
            sd_var = sd(mean_temp_sampling_period_5, na.rm = TRUE),
            median_var = median(mean_temp_sampling_period_5, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

@@

# Impute missing data; m = 10 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=10, maxit = 40,
                     method = c("polr", "logreg", "logreg", "logreg", "logreg",
                                "polr", "polr", "logreg", "logreg", "logreg",
                                "pmm", "pmm", "pmm", "polr", "pmm"))

write_rds(imputed_data, paste0(file_path, "Output/imputed_exposure_data_14may2020.rds"))

imputed_exposure_data <- read_rds(paste0(file_path, "Output/imputed_exposure_data_14may2020.rds"))

@@

write_rds(model_ave, paste0(file_path, "Output/imputed_exposure_model_14may2020.rds"))

exposure_model <- read_rds(paste0(file_path, "Output/imputed_exposure_model_14may2020.rds"))

@@

>>>>

```{r}
####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(home != "WMA300") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  # dichotomize variables by median value
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  mutate(home_act_door_2level = cut(home_act_door_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows_sum, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep_sum, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))
```

@@

# Select analysis vars
selected_vars <- analysis_data %>% 
  #filter(area == "NN") %>% 
  select(pm_mean_sampling_period,
         income_3level,
         residents_smoke,
         home_floors_2level, 
         home_sqft_2level,
         home_pets_2level,
         stove_age_3level, 
         chimney_clean_3level, 
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         stove_grade_3level,
         home_fireplace) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period)) %>%  
  select(-pm_mean_sampling_period) 
```

@@

# Check % missing data
mean(is.na(selected_vars)) # 10.7% for WMT

@@

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_grade_3level), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary
```

```{r}
# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(residents_smoke), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

@@

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_var = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_var = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_var = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_var = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

@@

# Impute missing data; m = 10 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=10, maxit = 40,
                     method = c("polr", "logreg", "logreg", "logreg", "logreg",
                                "polr", "polr", "logreg", "logreg", "pmm",
                                "pmm", "polr", "logreg", "pmm"))

write_rds(imputed_data, paste0(file_path, "Output/imputed_exposure_data_22may2020.rds"))

imputed_exposure_data <- read_rds(paste0(file_path, "Output/imputed_exposure_data_22may2020.rds"))

@@

write_rds(model_ave, paste0(file_path, "Output/imputed_exposure_model_22may2020.rds"))

exposure_model <- read_rds(paste0(file_path, "Output/imputed_exposure_model_22may2020.rds"))

@@

```{r}
# Look at R^2 for final selected model
model_results <- lm(log_pm_mean_sampling_period ~
                      residents_smoke +
                      chimney_clean_3level +
                      stove_grade_3level,
                      data = imputed_exposure_data$data)

summary(model_results)
```
